---
title: "Reading and saving data in R format"
output: html_notebook
---

I (Megan) have an excel file with assay data that I want to package, the data needs to be converted to .RData format to do so.

Load package for reading excel:
```{r}
library(readxl)
```

Read example excel file:
```{r}
StandardizationAssayData <- read_excel("StandardizationAssayData_example.xlsx")
```

Save RData:
```{r}
save(StandardizationAssayData, file = "StandardizationAssayData.RData")
```

Some examples of data visualization and manipulation

ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`)) + geom_point()
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`, color = `Samplle Vial`)) + geom_point()
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`, color = factor(`Samplle Vial`))) + geom_point()
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`)) + geom_point() + facet_wrap(~ `Samplle Vial`)
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`. color = "Identity")) + geom_point() + facet_wrap(~ `Samplle Vial`)
Error: unexpected symbol in "ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`."
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`, color = "Identity")) + geom_point() + facet_wrap(~ `Samplle Vial`)
> ggplot(data = StandardizationAssayData, aes(x = `Peak MT`, y = `Relative PA`, color = Identity)) + geom_point() + facet_wrap(~ `Samplle Vial`)
> load("C:/Users/megan/Documents/Reproducable research/R/R package/FirstRPackage/Raw/StandardizationAssayData.RData")
> View(StandardizationAssayData)

filter(StandardizationAssayData, `Samplle Vial` == 2)

select(StandardizationAssayData, `Samplle Vial`)

Note: Check `dplyr` and `ggplot2`

Note: Do a search for: r package build examples function not found
